Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-02-22 Thesis/01-chap1.Rmd
refine cubic model

Prolific provides an international participant pool with the option to apply flexible pre-screening filters. In this study, we recruited participants who was fluent in English with at least $10$ previous submissions and $98$% approval rate in other Prolific studies for quality control. Further, balance sample across gender was imposed to prevent gender bias.

@@

The study website was powered by Flask [@grinberg_flask_2018], a web framework written in Python 3 [@van_rossum_python_2009], hosted on PythonAnywhere [@pythonanywhere_pythonanywhere_2022], a web hosting service provider. Due to the limit of the storage on PythonAnywhere, lineup images needed for the website were hosted separately on Github Pages [@gtihub_github_2022-1], a static site hosting service provided by Github [@gtihub_github_2022], stored in private Github repositories. The uniform resource locator (URL) to lineup images were set to be unique random strings such that images can not be accessed by general approaches without knowing the correct URL. This avoided participants seeing the lineup beforehand. The front-end of the website was built using a JavaScript [@flanagan_javascript_2006] library jsPsych [@de_leeuw_jspsych_2015] which is specialized in creating online behavioral experiments. One of the reasons we chose to use this library was it had a modularized but highly customizable template which could record participant's response time automatically. This is essential for us to confirm the quality of the data by checking exceptionally fast or slow responses. Figure \@ref(fig:DiagramExperiment) summarizes the experiment setup.

@@

Lemma \@ref(lemma:cubic) shows that the expectation of the residuals is clearly a function of $\boldsymbol{X}$ and $\boldsymbol{Z}$. Hence, we would expect to see some patterns in the residual plot. Given the expectation of the residuals, we could plot the expected values of residuals against the observed values. Figure \@ref(fig:cubic1), \@ref(fig:cubic2) and \@ref(fig:cubic3) illustrate the shape of residuals under different parameter settings.

>>>>

Prolific provides an international participant pool with the option to apply flexible pre-screening filters. In this study, we recruited $62$ participants who was fluent in English with at least $10$ previous submissions and $98$% approval rate in other Prolific studies for quality control. Further, balance sample across gender was imposed to prevent gender bias.

@@

The study website was powered by Flask [@grinberg_flask_2018], a web framework written in Python 3 [@van_rossum_python_2009], hosted on PythonAnywhere [@pythonanywhere_pythonanywhere_2022], a web hosting service provider. Due to the limit of the storage on PythonAnywhere, lineup images needed for the website were hosted separately on Github Pages [@gtihub_github_2022-1], a static site hosting service provided by Github [@gtihub_github_2022], stored in private Github repositories. The uniform resource locator (URL) to lineup images were set to be unique random strings such that images can not be accessed by general approaches without knowing the correct URL. This avoided participants seeing the lineup beforehand. The front-end of the website was built using a JavaScript [@flanagan_javascript_2006] library jsPsych [@de_leeuw_jspsych_2015] which is specialized in creating online behavioral experiments. One of the reasons we chose to use this library was it had a modularized but highly customizable template which could record participant's response time automatically. This is essential for us to confirm the quality of the data by checking exceptionally fast or slow responses. Figure \@ref(fig:DiagramExperiment) summarizes the online experiment setup.

@@

Lemma \@ref(lemma:cubic) shows that the expectation of the residuals is clearly a function of $\boldsymbol{X}$ and $\boldsymbol{Z}$. Hence, we would expect to see some patterns in the residual plot. Let $X_i$ and $Z_i$, $i = 1,...,n$, be independent random variables follow uniform distribution $U(-1,1)$. Given the expectation of the residuals, we could plot the expected values of residuals against the observed values. Figure \@ref(fig:cubic1), \@ref(fig:cubic2) and \@ref(fig:cubic3) illustrate the shape of residuals and their expected values under different parameter settings.

### 2022-02-22 Thesis/_book/thesis.tex
refine cubic model

Prolific provides an international participant pool with the option to apply flexible pre-screening filters. In this study, we recruited participants who was fluent in English with at least \(10\) previous submissions and \(98\)\% approval rate in other Prolific studies for quality control. Further, balance sample across gender was imposed to prevent gender bias.

@@

The study website was powered by Flask \autocite{grinberg_flask_2018}, a web framework written in Python 3 \autocite{van_rossum_python_2009}, hosted on PythonAnywhere \autocite{pythonanywhere_pythonanywhere_2022}, a web hosting service provider. Due to the limit of the storage on PythonAnywhere, lineup images needed for the website were hosted separately on Github Pages \autocite{gtihub_github_2022-1}, a static site hosting service provided by Github \autocite{gtihub_github_2022}, stored in private Github repositories. The uniform resource locator (URL) to lineup images were set to be unique random strings such that images can not be accessed by general approaches without knowing the correct URL. This avoided participants seeing the lineup beforehand. The front-end of the website was built using a JavaScript \autocite{flanagan_javascript_2006} library jsPsych \autocite{de_leeuw_jspsych_2015} which is specialized in creating online behavioral experiments. One of the reasons we chose to use this library was it had a modularized but highly customizable template which could record participant's response time automatically. This is essential for us to confirm the quality of the data by checking exceptionally fast or slow responses. Figure \ref{fig:DiagramExperiment} summarizes the experiment setup.

@@

Lemma \ref{lemma:cubic} shows that the expectation of the residuals is clearly a function of \(\boldsymbol{X}\) and \(\boldsymbol{Z}\). Hence, we would expect to see some patterns in the residual plot. Given the expectation of the residuals, we could plot the expected values of residuals against the observed values. Figure \ref{fig:cubic1}, \ref{fig:cubic2} and \ref{fig:cubic3} illustrate the shape of residuals under different parameter settings.

@@

\begin{verbatim}
##             y          x          z          e      .resid   .fitted
## 1 -2.24847020  0.8783282 0.17687898  0.1539500  0.65761568 -2.906086
## 2 -3.85694079  0.9593166 0.30200008 -0.3526064 -0.45596841 -3.400972
## 3 -3.76887401  0.7677855 0.72090641 -0.4481692  0.56311185 -4.331986
## 4 -4.78398171  0.9238035 0.55802451 -0.8849474 -0.68606690 -4.097915
## 5  0.06998178 -0.7784446 0.02191688  0.2307539 -0.07869221  0.148674
\end{verbatim}

@@

\begin{verbatim}
## [1]  1.6431906  1.2501862 -1.9594998 -1.4124888  0.4786119
\end{verbatim}

>>>>

Prolific provides an international participant pool with the option to apply flexible pre-screening filters. In this study, we recruited \(62\) participants who was fluent in English with at least \(10\) previous submissions and \(98\)\% approval rate in other Prolific studies for quality control. Further, balance sample across gender was imposed to prevent gender bias.

@@

The study website was powered by Flask \autocite{grinberg_flask_2018}, a web framework written in Python 3 \autocite{van_rossum_python_2009}, hosted on PythonAnywhere \autocite{pythonanywhere_pythonanywhere_2022}, a web hosting service provider. Due to the limit of the storage on PythonAnywhere, lineup images needed for the website were hosted separately on Github Pages \autocite{gtihub_github_2022-1}, a static site hosting service provided by Github \autocite{gtihub_github_2022}, stored in private Github repositories. The uniform resource locator (URL) to lineup images were set to be unique random strings such that images can not be accessed by general approaches without knowing the correct URL. This avoided participants seeing the lineup beforehand. The front-end of the website was built using a JavaScript \autocite{flanagan_javascript_2006} library jsPsych \autocite{de_leeuw_jspsych_2015} which is specialized in creating online behavioral experiments. One of the reasons we chose to use this library was it had a modularized but highly customizable template which could record participant's response time automatically. This is essential for us to confirm the quality of the data by checking exceptionally fast or slow responses. Figure \ref{fig:DiagramExperiment} summarizes the online experiment setup.

@@

Lemma \ref{lemma:cubic} shows that the expectation of the residuals is clearly a function of \(\boldsymbol{X}\) and \(\boldsymbol{Z}\). Hence, we would expect to see some patterns in the residual plot. Let \(X_i\) and \(Z_i\), \(i = 1,...,n\), be independent random variables follow uniform distribution \(U(-1,1)\). Given the expectation of the residuals, we could plot the expected values of residuals against the observed values. Figure \ref{fig:cubic1}, \ref{fig:cubic2} and \ref{fig:cubic3} illustrate the shape of residuals and their expected values under different parameter settings.

@@

\begin{verbatim}
##             y          x          z          e     .resid     .fitted
## 1  0.44298045  0.1862316 -0.5114228  0.2749620  0.3561304  0.08685009
## 2 -0.46546366 -0.8542129 -0.3789133  0.3543143  0.2827120 -0.74817570
## 3  0.07636314  0.0383946 -0.3832281 -0.3024668 -0.2698449  0.34620801
## 4 -1.04762148 -0.4177674 -0.5876853 -0.3101100 -0.1202573 -0.92736416
## 5 -0.90198583 -0.5439192 -0.4630171 -0.1448947 -0.2487402 -0.65324563
\end{verbatim}

@@

\begin{verbatim}
## [1] -0.9369269  0.1945678  0.2816923 -0.3254415  0.7861083
\end{verbatim}
